---
title: "Qtlizer"
output: BiocStyle::html_document
author: "Julia Remes"
vignette: >
    %\VignetteIndexEntry{qtlizer}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

#Introduction 
The qtlizer package is written to provide the function of making a query 
to Qtilzer and obtain the results as a data frame.

#Add package to working directory
```{r setup}
library(Qtlizer)
```


#Example function calls
One can call the get_qtls function with a single query: 
```{r}
# Call get_qtls with a single query
get_qtls('rs4284742')
```

It is also possible to call the function 
with more than one query and a single string:
```{r}
# Call get_qtls with serveral queries
get_qtls('rs4284742, rs2070901')
```

Another possibility is to make a single request with a vector of queries:
```{r}
# Call get_qtls with serveral queries
df = get_qtls(c("rs4284742", "DEFA1"))
```

If many requests are to be made, 
a maximum of max_terms queries are made at once. 
This term can be changed manually (default is 10):
```{r}
# Get meta info
df2 = get_qtls(c("rs4284742", "DEFA1"), max_terms = 1)
```

There is meta info added to the returned data frame which can be accessed:
```{r}
# Get meta info
attributes(get_qtls("rs4284742")[[1]])
```
#Output of Session Info
Here is the output of ```sessionInfo()``` on the system 
on which this document was compiled: 
```{r}
sessionInfo()
```

