---
title: "qtlizer Package"
output: BiocStyle::html_document
author: "Julia Remes"
vignette: >
    %\VignetteIndexEntry{qtlizer}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---




```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

#Introduction 
The qtlizer package is written to provide the function of making a query 
to Qtilzer and obtain the results in a specified file.

#Add package to working directory
```{r setup}
library(qtilzerPackage)
```


#Example function calls
One can call the qtfun function with a single query: 
```{r}
# Call qtfun with a single query
qtfun('rs4284742')
```

It is also possible to call the function with more than one query:
```{r}
# Call qtfun with serveral queries
qtfun('rs4284742, rs2070901, DEFA1, ENSG00000122194, 
    hg19:19:45412079, hg38:6:12903725')
```

The first parameter will always be the query.

Optionally the name of the output file can 
be specified in a second parameter:
```{r}
# Call qtfun with a single query
qtfun('rs4284742', 'outputName.txt')
```

#Output of Session Info
Here is the output of ```sessionInfo()``` on the system 
on which this document was compiled: 
```{r}
sessionInfo()
```

